Beliefs about the development of mental life

### 2021-07-31 paper/paper.Rmd
add anonymized github repo

>>>>

Note: This is a fully reproducible manuscript, written in RMarkdown using the "knitr" package for R [@xie2021]. The full, editable script for all analyses, figures, and tables (here and in the Supplemental Materials) is available in the .Rmd file that generated this document, which can be found in the following GitHub repository: https://anonymous.4open.science/r/baby_mental_life_ms-C261/ (repo has been anonymized).
